

```{r}
---
#Article title: "R Markdown for the article : Ancient DNA and osteological analyses of a unique sub-fossil bone assemblage reveal Early Holocene faunal expansion into the Scandinavian Arctic"
#Section: "Building presence/absence matrix for PCR and subsamples test"
#Author of this script: "Aurélie Boilard"
#Institutional email : "aurelibo@uio.no"
#Personal email : "aurelie.boilard.1@outlook.com"
#Updated : "August 2023"
---


```{r}

#Activate the following R packages
library(tidyverse)
library(dplyr)
library(ggplot2)


##Load your data and metadata
metadata <- Metadata_NYMamp007
#Use cleaned tables to run the analysis on.
#Load NYMamp007_clean_AUGUST2023

#----------------------------------------------------------------------------------------------------------------------
#PCR REPLICATE PRESENCE/ABSENCE TABLE
#----------------------------------------------------------------------------------------------------------------------

#PCR repeat table
#Store the list of PCR replicate information of the metadata into an object.
pcr_rep  <- metadata$PCR_id
#Load your data into the reads_pcr object.
reads_pcr <- NYMamp007_clean_AUGUST2023
#Replace Group.1 with the sample information for this test.
reads_pcr$Group.1 <- pcr_rep
#Add the information of the PCR repeat number to the table.
reads_pcr$PCR_repeat <- metadata$PCR_repeat 
#It's not needed, technically, but in the next line, a column to disappears. It's basically a dummy.
pres_abs_pcr <- data.frame (ifelse(reads_pcr [,-(ncol(reads_pcr))]>0, 1, 0))
#
pres_abs_pcr$Group.1 <- pcr_rep
#Make sure you still have all the info you need.
#Save the presence/absence matrix as a csv.

write_csv(pres_abs_pcr, "YOUR_PATH/PCRrepeatsNYMampAUGUST2023.csv")

#----------------------------------------------------------------------------------------------------------------------
#BIOLOGICAL REPLICATE PRESENCE/ABSENCE TABLE
#----------------------------------------------------------------------------------------------------------------------


#Store the sample names for this test in an object.
bio_rep  <- metadata$Bio_rep
#Load your data
reads_biorep <- NYMamp007_clean_AUGUST2023
#Change the sample name
reads_biorep$Bio_rep <- bio_rep
#Get the PCR repeat information
reads_biorep$PCR <- metadata$PCR_repeat



#Select only samples of PCR repeat 1
reads_biorep_pcr1 <- subset(reads_biorep, PCR == 1)
#Store the sample names
bio_rep3 <-reads_biorep_pcr1$Group.1

#Now transform the reads count into a absence/presence matrix
pres_abs_BIO <- data.frame (ifelse(reads_biorep_pcr1 [,-(ncol(reads_biorep_pcr1))]>0, 1, 0))
#Get back the sample names
pres_abs_BIO$Group.1 <- bio_rep3

#Transpose in Excel and remove samples without pcr repeats.
write_csv(pres_abs, "YOUR_PATH/BIOrepeatsPCR1NYMamp007_AUGUST2023.csv")




```


```

