

```{r}
---
#Article title: "R Markdown for the article : Ancient DNA and osteological analyses of a unique sub-fossil bone assemblage reveal Early Holocene faunal expansion into the Scandinavian Arctic"
#Section: "Building a blast table"
#Author of this script: "Aurélie Boilard"
#Institutional email : "aurelibo@uio.no"
#Personal email : "aurelie.boilard.1@outlook.com"
#Updated : "August 2023"
---

```{r}


#Activate the following R packages
library(tidyverse)
library(dplyr)
library(ggplot2)

#Use readr to import dataset
#Filter to keep only what has over 98% identity for Mamp007, and 95% for Fish16S and Aves12S
#This markdown is an example for the Mamp007 primer.
taxo_2021 <- taxo_005_NOmam
taxo_2022 <- NO2022taxo_005_mam

taxo_raw_2021 <- taxo_2021[taxo_2021$`best_identity:mamp_feb2022` > 0.98,]
taxo_raw_2022 <- taxo_2022[taxo_2022$`best_identity:mamp_feb2022` > 0.98,]

taxo_final_2021 <- taxo_raw_2021[,c("id","best_identity:mamp_feb2022","count", "scientific_name", "species_list:mamp_feb2022", "species_name", "taxid", "sequence")]

taxo_final_2022 <- taxo_raw_2022[,c("id","best_identity:mamp_feb2022","count", "scientific_name", "species_list:mamp_feb2022", "species_name", "taxid", "sequence")]

taxo_all <- rbind(taxo_final_2021, taxo_final_2022) 

write_csv(taxo_all, "/Users/aurelibo/Documents/PhD/Projet/EvoCave/R/NOMamp007_blast.csv")



