

```{r}
---
#Article title: "R Markdown for the article : Ancient DNA and osteological analyses of a unique sub-fossil bone assemblage reveal Early Holocene faunal expansion into the Scandinavian Arctic"
#Section: "Building a blast table"
#Author of this script: "Aurélie Boilard"
#Institutional email : "aurelibo@uio.no"
#Personal email : "aurelie.boilard.1@outlook.com"
#Updated : "August 2023"
---

```{r}


#Activate the following R packages
library(tidyverse)
library(dplyr)
library(ggplot2)

#Use readr to import dataset
#Filter to keep only what has over 98% identity for Mamp007, and 95% for Fish16S and Aves12S
#This markdown is an example for the Mamp007 primer.
taxo_008 <- NY2021taxo_005_mamp007
taxo_raw <- taxo_008[taxo_008$`best_identity:mamp_feb2022` > 0.98,]
taxo_final <- taxo_raw[,c("id","best_identity:mamp_feb2022","count", "scientific_name", "species_list:mamp_feb2022", "species_name", "taxid", "sequence")]
write_csv(taxo_final, "/Users/aurelibo/Documents/PhD/Projet/EvoCave/R/Rerun_tables/NYMamp007_blast.csv")



